\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{examples/images/square_ring_results.png}
    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) and trapped flux inducing a circulating current of 1 mA (c, d). The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d). For the current plots (a, c), the colorscale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
    \label{fig:square-ring-results}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{examples/images/square_ring_results.png}
    \caption{Sheet current $\vec{J}(x, y)$ and out-of-plane magnetic field $\mu_0H_z(x, y)$ evaluated in the plane of a square ring with effective penetration depth $\Lambda=1\,\mu\mathrm{m}$ subject to a uniform applied field of 0.5 mT (a, b) and trapped flux inducing a circulating current of 1 mA (c, d). The sub-figures show the output of \inline{Solution.plot_currents()} (a, c) and \inline{Solution.plot_fields()} (b, d). For the current plots (a, c), the color-scale indicates the magnitude of the sheet current (or current density), $|\vec{J}|$, and the direction is indicated by the white streamlines.}
    \label{fig:square-ring-results}
\end{figure}
